Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-01 testbed.tex
fixed warning

hashmark (#) means to perform operation as root, dollar (\$) means to perform operation as user

@@

Mount root partition:
%\begin{lstlisting}[caption="Mount the root partition"]  % Start your code-block
\begin{lstlisting}[]  % Start your code-block

@@

Mount boot partition:
%\begin{lstlisting}[caption="Mount boot partition"]  % Start your code-block
\begin{lstlisting}[]  % Start your code-block

@@

We have installed the official Raspbian linux \ac{OS} on all the devices.

\subsection{Installation and Updating}
\subsection{Kodo cross-compilation: From your PC to the Raspberry Pi}

>>>>

hashmark (\#) means to perform operation as root, dollar (\$) means to perform operation as user

@@

Mount root partition:
%Mount the root partition
\begin{lstlisting}[]  % Start your code-block

@@

Mount boot partition:
%Mount boot partition
\begin{lstlisting}[]  % Start your code-block

@@

We can now change all the files in the disk image.

\subsection{Configuring OS files and scripts}

% Set hostname
\begin{lstlisting}[]  % Start your code-block

# echo "MrAwesome script" >> ${ROOTDIR}/etc/init.d/hostname.sh
\end{lstlisting}
\FloatBarrier

\subsection{Installation and Updating}

% CHROOT to OS image
\begin{lstlisting}[]  % Start your code-block

# mount ...
# chroot ${ROOTDIR}
\end{lstlisting}
\FloatBarrier

\subsection{Kodo cross-compilation: From your PC to the Raspberry Pi}
